---
title: 'Group Assignment #3'
author: "Group 5"
date: "13/5/2020"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(summarytools)

library(psych)
library(stargazer)
```

### Task
We want to explore the differences between the Orbis universe of German firms and the firms that filed for Insolvency in July and August. In order to do so, we perform three different steps. First, we limit the insolvency sample to firms who filed for insolvency. Second, we merge these firms algorithmically with the firms from the Orbis universe. Thereby, we are facing multiple issues that will be described below. Third, we define a set of informative variables to compare the insolvent firms with the others. 

### Step 1: Identifing firms that filed for insolvency in July and August
Read the data (following Joachim Gassen https://github.com/joachim-gassen/vhb_qear20/blob/master/code/describe_insolvency_data.Rmd).

```{r readData}
insol_raw <- read_csv(
  "../raw_data/insolvency_filings_de_julaug2020.csv",
  col_types = cols()
)
```

Select firms who filed for insolvency in July and August and delete duplicates.

```{r filter and deleteDups}
insol_op <- insol_raw %>% 
  filter(subject == "Eröffnungen") %>% 
  unique()
```

Check for missing values in insolvency data (following Joachim Gassen https://github.com/joachim-gassen/vhb_qear20/blob/master/code/describe_insolvency_data.Rmd).

```{r displayNAs}
na_vals <- insol_op %>%
  summarise_all(list( ~ sum(is.na(.))))

nas_df <- tibble(
  Variable = names(insol_op),
  `NA count` = t(na_vals)
)

kable(nas_df) %>% 
  kable_styling(full_width = FALSE)
```

That's nice! We do not have missing values. Therefore, we are now interested in how many firms actually filed for insolvency.

```{r NoofObs}
nrow(insol_op)
```

### Step 2: Merging insolvency data with data from orbis universe

After having identified all firms that filed for insolvency, we want to merge them with the Orbis data. Therefore, we first need to load the data (following Joachim Gassen https://github.com/joachim-gassen/vhb_qear20/blob/master/code/describe_insolvency_data.Rmd).

```{r readsecondData}
orbis_raw <- read_csv(
  "../raw_data/orbis_wrds_de.csv",
  col_types = cols()
)
```

As the Orbis data starts in the 90s, we want to restrict the observations to more recent periods. Therefore, we select only observations after 2015 and delete duplicates.

```{r filter and deleteDup}
orbis_de <- orbis_raw %>%
  filter(year > "2015") %>%
  unique()
```

In order to match the data with the insolvency data, we need to identify a key variable. As the insolvency data only contains the name of the filing firms, we need to rely on firm names for matching. This is not without problems because normally names are very noisy. Additionally, we should check whether every firms filed only once for insolvency (following Joachim Gassen https://github.com/joachim-gassen/vhb_qear20/blob/master/code/describe_insolvency_data.Rmd).

```{r NamesCourtFileNumber}
unique_firms <- insol_op %>%
  distinct(name_debtor, .keep_all = TRUE)

unique_firms %>%
  group_by(insolvency_court, court_file_number) %>%
  filter(n() > 1) %>%
  arrange(insolvency_court, court_file_number, name_debtor) %>%
  kable() %>%
  kable_styling()
```
As we can see, there are two firms who filed for insolvency twice. While one wonder how this might come, it sould not bother our analysis because we are only interested in whether the firm filed or not. 

##### Merging strategy
In order to merge both data sets based on firm names, we try to build a key variable which is less noisy against common speeling variations. Therefore, we create a new variable which is named "key" in both datasets which contains modified names by deleting white spaces, removing punctuation and transforming letters to lower cases.

```{r create key}
insolvency <- insol_op %>%
  mutate(key = name_debtor)

insolvency$key <- gsub("[[:space:]]", "", insolvency$key)
insolvency$key <- gsub("[[:punct:]]", "", insolvency$key)
insolvency$key <- tolower(insolvency$key)       

orbis <- orbis_de %>%
  mutate(key = name_native)

orbis$key <- gsub("[[:space:]]", "", orbis$key)
orbis$key <- gsub("[[:punct:]]", "", orbis$key)
orbis$key <- tolower(orbis$key) 
```

After creating the keys, we can merge both datasets with a left join. Additionally, we are creating a dummy variable "insolvency" which is 1 in the case of insolvency filing and 0 otherwise.
```{r mergeData}
merged_data <- left_join(orbis, insolvency, by = "key")

merged_data$insolvency <- ifelse(merged_data$subject == "Eröffnungen", 1, 0)
merged_data$insolvency[is.na(merged_data$insolvency)] <- 0
```

Delete unneeded variables.
```{r selectVar}
merged_data  <- merged_data  %>%
  select(-X1, -ctryiso, -key, -name_debtor)
```

Now, we want to explore for how many firms the merge was successfull.
```{r checkMerge}
table(merged_data$insolvency)
```
```{r countmatchedcases}
matched_cases <- merged_data %>%
  filter(insolvency == "1") %>%
  group_by(name_native) %>%
  count()
nrow(matched_cases)
```

This does not look nice. Out of 1042 insolvency cases, we could only match 270. 
##### Merging issues
As it is very unlikely that out of the 1042 insolvency cases, Orbis provide only data on 270 cases, we are facing two main merging issues. First, our merging strategy only addresses potential differences in names by punctuation, white spaces, and capital letter. Thereby, we are missing out on other differences like shortcuts etc. Additionally, it is possible that firms do have same names which means that we cannot differentiate who of them filed for insolvency. The second issue is illustrated by the following table.

```{r showmatchedcases}
merged_data %>%
  filter(insolvency == "1") %>%
  group_by(name_native)%>%
  count() %>%
  arrange(desc(n))%>%
  kable() %>%
  kable_styling()
```

### Step 3: Informative variables to compare the insolvent firms with solvent firms. 

#### We start with some basic descriptive tables showing the different characteristics of solvent and insolvent firms.

The following tables demonstrate the observations by industry. While Other Services amount for most observations in the solvent and insolvent subsample, followed by Wholesale and construction industry, the transport and metal product industry account for over 5% of insolvent cases. Especially, Food, beverages and tobacco, as well as, Wood, cork, paper, and Gas, Water, Electricity industries show the fewest cases of insolvency in our sample. 
```{r Tableindustry, include=FALSE}
sumtable1 <- merged_data %>%
  filter(insolvency == "1") %>%
  summarytools::freq(merged_data$major_sector, order = "freq")%>%
  as_tibble(rownames="rowname")

sumtable2 <- merged_data %>%
  filter(insolvency == "0" & year == 2018) %>%
  summarytools::freq(merged_data$major_sector, order = "freq")%>%
  as_tibble(rownames="rowname")
```
```{r Tableindustry1}
d.summary <- sumtable1 %>%
    select(industry=rowname, Freq, '% Total') %>%
    print()
```
```{r Tableindustry2}
d.summary <- sumtable2 %>%
    select(industry=rowname, Freq, '% Total') %>%
    print()
```


#### Based on the paper by Beaver et. al (2012) we decided to calcualte the following determinants: 

1) Profitability: Calculated by ROA
2) Loss year: Indicator for negative ROA in 2018
3) Leverage: Calculated by total liabilities / Total assets
4) Size: Calculated as ln of total assets

1) Profitability: Calculated by ROA (Should we use lagged toas?)
```{r Calculate ROA}
merged_data$roa <- merged_data$pl / merged_data$toas
```

2) Loss year: Indicator for negative ROA in 2018
```{r calculate Loss year dummy}
merged_data$loss <- ifelse(merged_data$roa < 0, 1, 0)
```

3) Leverage: Calculated by total liabilities / total assets
```{r calculate leverage as lta}
merged_data$lta <- (merged_data$ncli + merged_data$culi) / merged_data$toas
```

4) Size: Calculated as ln of total assets
```{r Calculate size}
merged_data$lntoas <- log(merged_data$toas)
```

Look at distribution of size

```{r distribution lntoas}
ggplot(merged_data, aes(x=lntoas)) +
    geom_histogram(colour="black", fill="white")
```

Quick check how many non missing values we have for the different determinants.
```{r}
sum( !is.na( merged_data$roa ) )
sum( !is.na( merged_data$loss ) )
sum( !is.na( merged_data$lta ) )
sum( !is.na( merged_data$lntoas ) )
```

Summary statistics of solvent and insolvent firms

```{r include=FALSE, summarytable}
d.summary.extended <- merged_data %>%
  select(cash, roa, lta, lntoas, empl) %>%
  psych::describe(quant=c(.25,.75)) %>%
  as_tibble(rownames="rowname")
```

```{r summary table short}
d.summary <- d.summary.extended %>%
    select(var=rowname, min, median, max, mean, sd) %>%
    print()
```


#### Next we calculate t-statistics to check for significant differences between the group of solvent and insolvent firms
```{r}
```


```{r}
```


```{r}
```


